Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-09 manuscript-figures.Rmd
lil fixes
use high res Topt values for R0 heatmaps

# Vector trait TPC data
data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
  #
  pathosystem_labeller()
# R0 data
# !!! [] needs to be updated to include 1e-1, 1e0, 1e1
data.R0_TPCs <- read_ds("results/R0_TPC_vals.rds") %>%
  pathosystem_labeller()

@@

# Compute *mosquito* thermal tolerance range (minimum and maximum)
MosqThermRange_df <- median.Vec %>%
  pathosystem_labeller() %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()
```

@@

@@

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    breaks = fill_breaks
  ) +
  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    breaks = fill_breaks
  ) +
  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +
  # Topt curve:
  geom_line(
    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
    mapping = aes(
      x = sigmaH_proxy,
      y = Topt,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +
  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels,
    expand = c(0, 0)
  ) +
  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(16, 35),
    breaks = seq(10, 36, by = 2)
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +
  # faceting:
  facet_rep_grid(
    rows = vars(KH),
    cols = vars(system_label),
    labeller = labeller(.rows = mylabels),
    repeat.tick.labels = "left"
  ) +
  # theme options:
  theme_minimal_hgrid() +
  theme(
    axis.line = element_line(),
    panel.spacing = unit(1, "lines"),
    legend.text = element_text(size = 11),
    legend.text.align = 0,
    strip.text = ggtext::element_markdown(
      size = 8,
      hjust = 0
    )
  )

>>>>

# Vector trait TPC data
data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
  #
  pathosystem_labeller()
# R0 data
# !!! [] needs to be updated to include 1e-1, 1e0, 1e1
data.R0_TPCs <- read_rds("results/R0_TPC_vals.rds") %>%
  pathosystem_labeller()

@@

# Compute *mosquito* thermal tolerance range (minimum and maximum)
MosqThermRange_df <- mean.Vec %>%
  pathosystem_labeller() %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()
```

@@

Topt_for_R0_df <- data.Topt %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, median) %>%
  mutate(sigmaH_proxy = sigmaH)
Topt_for_R0_df <- inf_skew_func(Topt_for_R0_df, infinite_skew, infinite_divide, 8)

@@

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    mapping = aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    mapping = aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
  # Topt curve:
  geom_path(
    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)),
    mapping = aes(
      x = sigmaH_proxy,
      y = median,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +
  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels,
    expand = c(0, 0)
  ) +
  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(16, 35),
    breaks = seq(10, 36, by = 2)
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +
  # faceting:
  facet_rep_grid(
    rows = vars(KH),
    cols = vars(system_label),
    labeller = labeller(.rows = mylabels),
    repeat.tick.labels = "left"
  ) +
  # theme options:
  theme_minimal_hgrid(11) +
  theme(
    axis.line = element_line(),
    panel.spacing = unit(1, "lines"),
    legend.text = element_text(size = 11),
    legend.text.align = 0,
    strip.text = ggtext::element_markdown(
      size = 8,
      hjust = 0
    )
  )
